---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  cache = TRUE,
  fig.path = "inst/"
)
```

# Welcome to ReHeaT

<!-- badges: start -->
[![Build Status](https://travis-ci.com/saezlab/reheat.svg?branch=master)](https://travis-ci.com/saezlab/reheat)
<!-- badges: end -->

>the **Re**ference for the **Hea**rt failure **T**ranscriptome


### About
ReHeaT is a user friendly portal to explore, analyze and download the transcriptional consensus signature of human end-stage heart failure (HF-CS).

The HF-CS is based on a [meta-analysis](https://www.medrxiv.org/content/10.1101/2020.05.23.20110858v1) of 16 independent studies. Corresponding code is available [here](https://github.com/saezlab/HF_meta-analysis).

### How to access

There are basically three ways of how to access ReHeaT:

* You can access a live version running [here](https://saezlab.shinyapps.io/reheat/) on the server from `shinyapps.io`.

* You can run the app locally in an interactive R session. Before make sure you have all packages installed listed in [`sub/global.R`](https://github.com/saezlab/reheat/blob/master/sub/global.R).
```{r, eval=FALSE}
shiny::runGitHub("reheat", "saezlab")
```

* You can run the app locally by cloning this repository. All required packages can be easily installed using the [`renv`](https://rstudio.github.io/renv/index.html) package.
```{r, eval=F}
# install all required packages using the renv package
renv::restore()
shiny::runApp()
```

